An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/intro.tex
config: impl

Secondly, without templates, learning rules and constraints is a challenge. 
\ennan{Here, we need to add one-paragraph description 
to illustrate how we learn rules without templates, 
or why we say our learning results are better than existing
learning approach, \eg, EnCore.}

>>>>

Second, without templates, learning rules and constraints is 
another challenge.
Rather than relying on pre-defined templates or 
manually correcting training set,
we introduce and perform probabilistic learning approaches 
on probabilistically typed representations
generated in the transformation phase.
The learning process first analyzes the occurrences of each pair
of entries in the training set, 
then computes the likelihood that each pair can constitute a rule, 
and finally derive many rules.
